---
title: "Mannheimia haemolytica Analysis Report" 
date: "`r Sys.Date()`"
output: html_document
params:
  card: ""
  geno: ""
  sero: ""
  vf: ""
  
---


<br>

## Predicted AMR genes from CARD database
Predicted using abricate tool with CARD database as option. For more info please see https://github.com/tseemann/abricate and https://card.mcmaster.ca/
```{r, echo=FALSE}

abricate_raw <- read.csv(params$card,header = TRUE,sep = "\t")
abricate_final <- abricate_raw[,c(2,6,10,11,15)]
colnames(abricate_final) <- c("SEQUENCE","GENE","%COVERAGE","%IDENTITY","RESISTANCE")
knitr::kable(abricate_final,align = "lcccr")
```

<br>

## Genotyping
Predicted based on presence(Genotype-2) or absence (Genotype-1) Adhesin G gene.based on this publication Clawson et al. BMC Microbiology (2020) 20:250 https://rdcu.be/dmIsH
```{r, echo=FALSE}

genotype_final <- read.csv(params$gen,header = TRUE, sep = '\t')

knitr::kable(genotype_final,align = "lc")

```


<br>

## Capsular Serotyping

Capsular serotyping of Mannheimia haemolytica serotypes 1, 2, and 6.For more info please see https://doi.org/10.1016/j.mimet.2017.05.010

```{r, echo=FALSE}

serotype_final <- read.csv(params$sero,header=TRUE,sep = '\t')

knitr::kable(serotype_final,align = "lc")

```

<br>

## Virulence factors

Virulence factors https://doi.org/10.1111/j.1574-6968.2006.00460.x
```{r, echo=FALSE}

vf <- read.csv(params$vf,header=FALSE,sep = '\t')

vf_final <- vf[,c(1,4)]

knitr::kable(vf_final,align = "lc")

```




